A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-09-04 paper/paper.methods.tex
Work on fixing discussion
- Remove/simplify discussion of NP-hardness
- Add more detail to impact of formulation on clinicians, hospital dept. w/citation
- Clean up ILP abbreviation throughout paper
Minor typo and other fixes

In this section, we present an application of integer linear programming to solve the clinician scheduling problem presented in Section \ref{sec:problem}. First, we describe the sets, indices and variables present in the formulation of the program. We then convert the constraints given in Table \ref{tbl:constraint-summary} into mathematical terms, and outline the objective function of the linear program.

@@

The Block-Weekend Adjacency is optimized by considering the product $X_{c, b, s}\cdot Y_{c, w}$ for values of $w$ ``adjacent'' to the value of $b$. This leads to the maximization objective %avoid editorial adjectives
\begin{align}
&Q_3(X, Y) = \sum_{c=1}^{C} \sum_{b=1}^{B} \sum_{s=1}^{S} X_{c, b, s}\cdot Y_{c, w=\varphi(b)} \tag{BWA} \label{eqn:obj-block-weekend-adj}
\end{align}
where $\varphi(b)$ maps a block one-to-one to an adjacent weekend, by some appropriate definition of adjacency. For instance, clinicians might want to be assigned during a weekend that falls within an assigned block. In this case, we will have $\varphi(b) = 2b-1$. \\

>>>>

In this section, we present an application of ILP to solve the clinician scheduling problem presented in Section \ref{sec:problem}. First, we describe the sets, indices and variables present in the formulation of the program. We then convert the constraints given in Table \ref{tbl:constraint-summary} into mathematical terms, and outline the objective function of the linear program.

@@

The Block-Weekend Adjacency is optimized by considering the product $X_{c, b, s}\cdot Y_{c, w}$ for values of $w$ ``adjacent'' to the value of $b$. This leads to the maximization objective %avoid editorial adjectives
\begin{align}
&Q_3(X, Y) = \sum_{c=1}^{C} \sum_{b=1}^{B} \sum_{s=1}^{S} X_{c, b, s}\cdot Y_{c, w=\varphi(b)} \tag{BWA} \label{eqn:obj-block-weekend-adj}
\end{align}
where $\varphi(b)$ is a one-to-one mapping of a block to an adjacent weekend, by some appropriate definition of adjacency. For instance, clinicians might want to be assigned during a weekend that falls within an assigned block. In this case, we will have $\varphi(b) = 2b-1$. \\
